Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2018-09-07 tex/WW4C_VHzQ.tex
Update WW4C_VHzQ.tex
Updated discussion about processing of aperture photometry and averaging

    Add table?
    \begin{table*}
      \begin{center}
        \setlength{\tabcolsep}{4pt}
        \begin{tabular}{lll lll lll l}
          \hline \hline
          &  programmeID &	mapID &	setupID  &	description               &	useDeeps  &	useHighProd &	timeScale	    &  nEpochs     &	overLaps\\
          \hline
          1	& 10999	           &    1       &	1            &      Average over a week	 &     0        & 	NONE            &	+7.000000  &	-99999999 &	0\\
          2	& 10999             & 	 1	  & 2   	     & Average over a fortnight &	0        &	NONE	&+14.000000	&-99999999 &	0\\
          3	& 10999	           &    1  	 & 3	             & Average over a month	&      0        &	NONE	&+30.000000	&-99999999 &	0\\
          4	& 10999             & 	 1	 & 4	              & Average over 10 epochs &	0        &	NONE	&-9.999995E008 &	10 &	0\\
          5	& 10999             &	 1	 & 5	             & Average over 6 months   &	0        &	NONE	&+183.000000 &	-99999999 &	0\\
          6	& 10999            &	 1	 & 6	           & Average over whole time  &	0        &	NONE	&-1.000000 &	-99999999 &	0\\
          \hline \hline
          \label{tab:The_Numbers}
        \end{tabular}
        \caption{}
      \end{center}
    \end{table*}

    \subsubsection{Processing MAP data and Forced photometry} 
    A set of apertureIDs were created in \verb+MapApertureIDshighzQsoMap+, based on
    the \verb+RequiredMatchedApertureProduct+ {\bf selection} value. This may
    seem unnecessary layer since it is a one-to-one match with \verb+finalQsoCatalogue+,
    but the layer is a general abstraction that allows multiple sources of
    catalogue, and multiple types\ldots
    Entries added to \verb+MapSurveyTables+ $\Rightarrow$ not pertinent

    CASU's \verb+imcore_list+ was run on each frame assigned to the programme with
    the input list equal to objects selected to be within \ldots of the multiframe
    centre. In this case, where there are 424 QSOs spread across the sky, there is
    typically 1 object per multiframe, but many have two and one,
    multiframeID=2614475 in the VSA, has 3 objects. The output of \verb+imcore_list+
    is a multi-extension FITS binary table, with identical columns to the CASU FITS
    binary tables produced using the CASU \verb+imcore+, the basis of all WFCAM and
    VISTA survey products and also familiar to many astronomers through the INTWFS, 
    VST-ATLAS and VPHAS.     {\it this needs tidied up, citations added...}
    Since forced photometry can be run
    in many ways on a particular image, a single science frame is not
    necessarily linked to a single MAP catalogue, so the \verb+MapFrameStatus+ table
    links images ({\bf multiframeID}) to catalogues ({\bf catalogueID}) and gives
    information on what processing stage they are at ({\bf bitProcessingFlag}),
    whether they have been ingested ({\bf isIngested}), or what quality control has
    been run on them ({\bf ppErrBitsStatus}).

    For matched aperture measurements, we process these binary tables using the same
    software, as the standard extracted catalogues, but implement a few different
    processes. We calculate both Luptitudes \citep{Luptitudes}, and calibrated fluxes,
    see Eqn~\ref{eq:jky}.

@@

    Quasars are known to vary (both photometrically and spectroscopically)
and very high-$z$ quasars under going super-Eddington accretion during
a rapid BH growth phase are prime candidates for this variation.
Therefore, with repeat observations over many epochs available via the
WSA, we have a choice to make for how we report the photometry. After
tests, we decide to give the NIR photometry averaged on 4 week
observed timescales. This time bracket is chosen as a good compromise
between maximising signal-to-noise while keeping the cadence high. At
our observed redshifts, we sample $\lesssim1$week in the rest-frame
and luminous quasars are not expected to vary on timescales quicker
than this \citep[e.g., ][]{Lawrence2016_ASPC}.

    \subsubsection{Averaging matched photometry}
    Unfortunately the photometry in a single epoch image often has low
    signal-to-noise. The advantage of matched aperture photometry on QSOs is that
    co-adding is relatively simple: if each epoch is taken in the same aperture
    (assuming the astrometry is correct) and the aperture photometry has been
    corrected to total: the standard aperture corrections work well for point
    sources then averaging the calibrated photometry should give as good as
    extracting from a deep stack. In fact it will almost certainly do better, since
    the images in some cases are taken from multiple projects with different
    pointings. In addition, corrections such as scattered light, pixel distortion
    and aperture corrections will be more complex, if not impossible to apply to
    deep-stacks but will be automatically applied in the averaging of forced
    photometry.

@@

    We calculate a set of averaged catalogues, for each pointing and filter, based
    on the requirements in \verb+RequiredMapAverages+, in these cases over time
    spans of 7, 14, 28, 183 days, over 10 epochs and finally over all epochs. The
    averaging process starts at the first epoch and works on. Possible future
    refinements could first look for denser groupings that satisfied the criteria so
    that these were not split into two groups.

@@

    The code to calculate variability statistics as described in \cite{Cross2009} has
    not yet been completed to run with the matched aperture pipeline, so these are
    not included.

>>>>

    Add table?
    \begin{table*}
      \begin{center}
        \setlength{\tabcolsep}{4pt}
        \begin{tabular}{lll lll lll l}
          \hline \hline
          &  programmeID &	mapID &	setupID  &	description               &	useDeeps  &	useHighProd &	timeScale	    &  nEpochs     &	overLaps\\
          \hline
          1	& 10999	           &    1       &	1            &      Average over a week	 &     0        & 	NONE            &	+7.000000  &	-99999999 &	0\\
          2	& 10999             & 	 1	  & 2   	     & Average over a fortnight &	0        &	NONE	&+14.000000	&-99999999 &	0\\
          3	& 10999	           &    1  	 & 3	             & Average over a month	&      0        &	NONE	&+30.000000	&-99999999 &	0\\
          4	& 10999             & 	 1	 & 4	              & Average over 10 epochs &	0        &	NONE	&-9.999995E008 &	10 &	0\\
          5	& 10999             &	 1	 & 5	             & Average over 6 months   &	0        &	NONE	&+183.000000 &	-99999999 &	0\\
          6	& 10999            &	 1	 & 6	           & Average over whole time  &	0        &	NONE	&-1.000000 &	-99999999 &	0\\
          \hline \hline
          \label{tab:reqMapAvg}
        \end{tabular}
        \caption{}
      \end{center}
    \end{table*}

    \subsubsection{Processing MAP data and Forced photometry} 
    A set of apertures to do forced photometry with were created in 
    \verb+MapApertureIDshighzQsoMap+, based on the \verb+RequiredMatchedApertureProduct+ 
    {\it selection} value, which in this case is to use the known positions of $z>5$ QSOs. This may
    seem unnecessary layer since it is a one-to-one match with \verb+finalQsoCatalogue+,
    but the layer is a general abstraction that allows multiple selections of data, including complex queries
    or input images.

    CASU's \verb+imcore_list+ was run on each frame assigned to the programme with
    the input list equal to objects selected to be within \ldots of the multiframe
    centre. In this case, where there are 424 QSOs spread across the sky, there is
    typically 1 object per multiframe, but many have two and one frame,
    multiframeID=2614475 in the VSA (a J-band stack from a P90 PI programme), has 3 objects. 
    The output of \verb+imcore_list+
    is a multi-extension FITS binary table, with identical columns to the CASU FITS
    binary tables produced using the CASU \verb+imcore+\footnote{http://casu.ast.cam.ac.uk/surveys-projects/vista/technical/catalogue-generation}, the basis of all WFCAM and
    VISTA survey catalogue products and also familiar to many astronomers through the INTWFS, 
    VST-ATLAS and VPHAS. Since forced photometry can be run
    in many ways on a particular image depending on the input catalogue, a single science frame is not
    necessarily linked to a single MAP catalogue, so the \verb+MapFrameStatus+ table
    links images ({\bf multiframeID}) to catalogues ({\bf catalogueID}).
    For matched aperture measurements, we process these binary tables using the same
    software, as the standard extracted catalogues, but implement a few different
    processes. We calculate both Luptitudes \citep{Luptitudes}, and calibrated fluxes,
    see Eqn~\ref{eq:jky}.

@@

    Quasars are known to vary (both photometrically and spectroscopically)
and very high-$z$ quasars under going super-Eddington accretion during
a rapid BH growth phase are prime candidates for this variation. [NJC: This is better placed somewhere else. We first used it to justify averaging over ~4 weeks, but then decided to average over many periods and select later.]
Therefore, with repeat observations over many epochs available via the
WSA, we have a choice to make for how we report the photometry. The remeasured photometry is averaged to
improve signal-to-noise over all the averaging schemes setup in Table~\ref{tab:reqMapAvg}. This allows us to get the best combination of signal-to-noise and number of epochs for different QSOs.

    \subsubsection{Averaging matched photometry}
    Unfortunately the photometry in a single epoch image often has low
    signal-to-noise. The advantage of matched aperture photometry on QSOs is that
    co-adding is relatively simple: if each epoch is taken in the same aperture
    (assuming the astrometry is correct) and the aperture photometry has been
    corrected to total: the standard aperture corrections work well for point
    sources then averaging the calibrated photometry should give as good as
    extracting from a deep stack. In fact it will almost certainly do better, since
    the images in some cases are taken from multiple projects with different
    pointings, and orientations and exposures, so stacking may not be optimal. 
    In addition, corrections such as scattered light, pixel distortion
    and aperture corrections will be more complex, if not impossible to apply to
    deep-stacks but will be automatically applied in the averaging of forced
    photometry.

@@

    We calculate a set of averaged catalogues, for each pointing and filter, based
    on the requirements in \verb+RequiredMapAverages+, in these cases over time
    spans of 7, 14, 30, 91, 183 days, 365 days, 730 days, over 10 epochs and over all epochs,
    see Tab.~\ref{tab:reqMapAvg}. The
    averaging process starts at the first epoch and works on. Possible future
    refinements could first look for denser groupings that satisfied the criteria so
    that these were not split into two groups. For this high-z QSO project we have averaged over overlaps, 
    because in several cases data for one source comes from multiple original projects that have slightly 
    different pointings.

@@

    The code to calculate variability statistics as described in \cite{Cross2009} has
    not yet been completed to run with the matched aperture pipeline, so these are
    not included. Variables were selected ...
